---
title: "DBA Proj- Wm"
output: html_document
date: "2023-03-29"
---

For this project, we assume that the exchange rate are as follows:
1 CAD is 0.98 SGD

# Web Scrapping of On-campus Data
## Orchard Commons
```{r}
library(XML)
library(curl)
library(tidyverse)
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/orchard-commons/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)

oc_fees <- as.data.frame(data[1]) %>% drop_na()
colnames(oc_fees) <- c("Room.Type", "Room", "Meal.Plan", "Total")
oc_fees$Type <- "Winter Session Contract"
oc_fees$Type[c(5,6,7,8)] <- "Term 1 Only"
oc_fees$Type[c(9,10,11,12)] <- "Term 2 Only"

#remove additional indications
oc_fees$Room.Type <- gsub("\\*", "", oc_fees$Room.Type)

#change price related columns to numeric
oc_fees$Room <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", oc_fees$Room)))

oc_fees$Meal.Plan <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", oc_fees$Meal.Plan)))

oc_fees$Room <- as.numeric(oc_fees$Room)
oc_fees$Meal.Plan <- as.numeric(oc_fees$Meal.Plan)

#change the currency
oc_fees$Room <- oc_fees$Room/ 0.98
oc_fees$Meal.Plan <- oc_fees$Meal.Plan/ 0.98

oc_fees$Total <- oc_fees$Room + oc_fees$Meal.Plan
oc_fees$Accom <- "Orchard Commons"

#final dataframe
head(oc_fees, 5)
```

## Place Vanier
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/place-vanier/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)

pv_fees <- as.data.frame(data[1]) %>% drop_na()
colnames(pv_fees) <- c("Room.Type", "Room", "Meal.Plan", "Total")

pv_fees$Type <- "Winter Session Contract"
pv_fees$Type[c(6,7,8,9,10)] <- "Term 1 Only"
pv_fees$Type[c(11,12,13,14,15)] <- "Term 2 Only"

#change price related columns to numeric
pv_fees$Room <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", pv_fees$Room)))

pv_fees$Meal.Plan <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", pv_fees$Meal.Plan)))

pv_fees$Room <- as.numeric(pv_fees$Room)
pv_fees$Meal.Plan <- as.numeric(pv_fees$Meal.Plan)

#change the currency
pv_fees$Room <- pv_fees$Room/ 0.98
pv_fees$Meal.Plan <- pv_fees$Meal.Plan/ 0.98

pv_fees$Total <- pv_fees$Room + pv_fees$Meal.Plan
pv_fees$Accom <- "Place Vanier"

#final dataframe
head(pv_fees, 5)

```

## Totem Park
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/totem-park/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
tp_fees <- as.data.frame(data[1]) %>% drop_na()
colnames(tp_fees) <- c("Room.Type", "Room", "Meal.Plan", "Total")

tp_fees$Type <- "Winter Session Contract"
tp_fees$Type[12:22] <- "Term 1 Only"
tp_fees$Type[23:33] <- "Term 2 Only"

#change price related columns to numeric
tp_fees$Room <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", tp_fees$Room)))

tp_fees$Meal.Plan <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", tp_fees$Meal.Plan)))

tp_fees$Room <- as.numeric(tp_fees$Room)
tp_fees$Meal.Plan <- as.numeric(tp_fees$Meal.Plan)

#change the currency
tp_fees$Room <- tp_fees$Room/ 0.98
tp_fees$Meal.Plan <- tp_fees$Meal.Plan/ 0.98

tp_fees$Total <- tp_fees$Room + tp_fees$Meal.Plan

#remove additional indications
tp_fees$Room.Type <- gsub("\\*", "", tp_fees$Room.Type)

tp_fees$Accom <- "Totem Park"

#final dataframe
head(tp_fees, 5)

```

## Brock Commons
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/brock-commons-tallwood-house-fees/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
bc_fees <- as.data.frame(data[1]) %>% drop_na() 

bc_fees_cleaned <- bc_fees[4,2:3]

colnames(bc_fees_cleaned) <- c("Studio.Suite", "4.Bedroom.Suite")

bc_fees_cleaned <- gather(bc_fees_cleaned, key="Room.Type", value="Total")

#change price related columns to numeric
bc_fees_cleaned$Total <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", bc_fees_cleaned$Total)))

bc_fees_cleaned$Total <- as.numeric(bc_fees_cleaned$Total)

#change the currency
bc_fees_cleaned$Total <- bc_fees_cleaned$Total/ 0.98

#remove additional indications
bc_fees_cleaned$Room.Type <- gsub("\\.", " ", bc_fees_cleaned$Room.Type)
bc_fees_cleaned$Accom <- "Brock Commons"

#final dataframe
head(bc_fees_cleaned, 5)

```

## Exchange
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/exchange-fees/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
exchange_fees <- as.data.frame(data[1]) %>% drop_na() 
exchange_fees <- exchange_fees[4,]

exchange_fees_cleaned <- gather(exchange_fees, key="Room.Type", value="Total")
exchange_fees_cleaned <- exchange_fees_cleaned[2:7, ]

#change price related columns to numeric
exchange_fees_cleaned$Total <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", exchange_fees_cleaned$Total)))

exchange_fees_cleaned$Total <- as.numeric(exchange_fees_cleaned$Total)

#change the currency
exchange_fees_cleaned$Total <- exchange_fees_cleaned$Total/ 0.98

#remove additional indications
exchange_fees_cleaned$Room.Type <- gsub("\\.", " ", 
                                  gsub("NULL.", "", exchange_fees_cleaned$Room.Type))

exchange_fees_cleaned$Accom <- "Exchange"

#final dataframe
head(exchange_fees_cleaned, 5)

```


## Fairview Crescent
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/fairview-crescent/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
fc_fees <- as.data.frame(data[1]) %>% drop_na() 
fc_fees <- fc_fees[c(4, 8, 10), -1]


fc_fees_cleaned <- gather(fc_fees, key="Room.Type", value="Total")
fc_fees_cleaned$Type <- c("Winter Session Contract", "Term 1 Only", "Term 2 Only")

fc_fees_cleaned$Room.Type <- gsub("\\.", " ", 
                                  gsub("NULL.", "", fc_fees_cleaned$Room.Type))

#change price related columns to numeric
fc_fees_cleaned$Total <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", fc_fees_cleaned$Total)))

fc_fees_cleaned$Total <- as.numeric(fc_fees_cleaned$Total)

#change the currency
fc_fees_cleaned$Total <- fc_fees_cleaned$Total/ 0.98

fc_fees_cleaned$Accom <- "Fairview Crescent"

#final dataframe
head(fc_fees_cleaned, 5)

```

## Fraser Hall
Only offers 1 type of Housing Type
```{r}
fh_fees <- as.data.frame(list(Room.Type = "Six Bedroom", Total=10802.82/0.98, Accom = "Fraser Hall"))
```

## Iona House
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/iona-house-fees/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
ih_fees <- as.data.frame(data[1]) %>% drop_na() 
ih_fees <- ih_fees[4, -1]


ih_fees_cleaned <- gather(ih_fees, key="Room.Type", value="Total")

ih_fees_cleaned$Room.Type <- gsub("\\.", " ", 
                                  gsub("NULL.", "", ih_fees_cleaned$Room.Type))

#change price related columns to numeric
ih_fees_cleaned$Total <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", ih_fees_cleaned$Total)))

ih_fees_cleaned$Total <- as.numeric(ih_fees_cleaned$Total)

#change the currency
ih_fees_cleaned$Total <- ih_fees_cleaned$Total/ 0.98

ih_fees_cleaned$Accom <- "Iona House"

#final dataframe
head(ih_fees_cleaned, 5)

```

## Marine Drive 
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/marine-drive/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
md_fees <- as.data.frame(data[1]) %>% drop_na() 
md_fees <- md_fees[4, -1]

md_fees_cleaned <- gather(md_fees, key="Room.Type", value="Total")

md_fees_cleaned$Room.Type <- gsub("\\.", " ", 
                                  gsub("NULL.", "", md_fees_cleaned$Room.Type))

#change price related columns to numeric
md_fees_cleaned$Total <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", md_fees_cleaned$Total)))

md_fees_cleaned$Total <- as.numeric(md_fees_cleaned$Total)

#change the currency
md_fees_cleaned$Total <- md_fees_cleaned$Total/ 0.98

md_fees_cleaned$Accom <- "Marine Drive"

#final dataframe
head(md_fees_cleaned, 5)

```

## Ponderosa Commons 
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/ponderosa-commons/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
pc_fees <- as.data.frame(data[1]) %>% drop_na() 
pc_fees <- pc_fees[4, -1]

pc_fees_cleaned <- gather(pc_fees, key="Room.Type", value="Total")

pc_fees_cleaned$Room.Type <- gsub("\\.", " ", 
                                  gsub("NULL.", "", pc_fees_cleaned$Room.Type))

#change price related columns to numeric
pc_fees_cleaned$Total <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", pc_fees_cleaned$Total)))

pc_fees_cleaned$Total <- as.numeric(pc_fees_cleaned$Total)

#change the currency
pc_fees_cleaned$Total <- pc_fees_cleaned$Total/ 0.98

pc_fees_cleaned$Accom <- "Ponderosa Commons"

#final dataframe
head(pc_fees_cleaned, 5)

```

## The Houses of the Ones Belonging to the Saltwater
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/houses-of-ones-belonging-to-saltwater-fees/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
sw_fees <- as.data.frame(data[1]) %>% drop_na() 
sw_fees <- sw_fees[4, -1]

sw_fees_cleaned <- gather(sw_fees, key="Room.Type", value="Total")

sw_fees_cleaned$Room.Type <- gsub("\\.", " ", 
                                  gsub("NULL.", "", sw_fees_cleaned$Room.Type))

#change price related columns to numeric
sw_fees_cleaned$Total <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", sw_fees_cleaned$Total)))

sw_fees_cleaned$Total <- as.numeric(sw_fees_cleaned$Total)

#change the currency
sw_fees_cleaned$Total <- sw_fees_cleaned$Total/ 0.98

sw_fees_cleaned$Accom <- "The Houses of the Ones Belonging to the Saltwater"

#final dataframe
head(sw_fees_cleaned, 5)

```

## Ritsumeikan-UBC House
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/ritsumeiken-ubc/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
r_fees <- as.data.frame(data[1]) %>% drop_na() 
r_fees <- r_fees[c(4, 7, 8), -1]

r_fees_cleaned <- gather(r_fees, key="Room.Type", value="Total")

#add room type
r_fees_cleaned$Type <- c("Winter Session Contract", "Term 1 Only", "Term 2 Only")

r_fees_cleaned$Room.Type <- gsub("\\.", " ", 
                                  gsub("NULL.", "", r_fees_cleaned$Room.Type))

#change price related columns to numeric
r_fees_cleaned$Total <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", r_fees_cleaned$Total)))

r_fees_cleaned$Total <- as.numeric(r_fees_cleaned$Total)

#change the currency
r_fees_cleaned$Total <- r_fees_cleaned$Total/ 0.98

r_fees_cleaned$Accom <- "Ritsumeikan-UBC House"

#final dataframe
head(r_fees_cleaned, 5)

```

## Thunderbird
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/thunderbird/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
tb_fees <- as.data.frame(data[1]) %>% drop_na() 
colnames(tb_fees) <- c("Room.Type", "Unit.Square.Foot", "Total")
tb_fees <- tb_fees[-1,]
#assumes that the prices are per student
tb_fees$Total <- gsub("/person", "", tb_fees$Total)

#clean the room size column 
library(tidyverse)
tb_fees <- tb_fees %>% separate(col=Unit.Square.Foot, into=c("Min.Unit.Square.Foot", "Max.Unit.Square.Foot"), sep="-")

#change price related columns to numeric
tb_fees$Total<- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", tb_fees$Total)))

tb_fees$Total <- as.numeric(tb_fees$Total)

#change the currency
tb_fees$Total <- (tb_fees$Total/ 0.98)*12

tb_fees$Accom <- "Thunderbird"

#final dataframe
head(tb_fees, 5)

```

## Walter Gage
```{r}
theurl<-"https://vancouver.housing.ubc.ca/applications/fees-payments/walter-gage/"
url <- curl(theurl)
urldata<-readLines(url)
data<-readHTMLTable(urldata,stringAsFactors=FALSE)
  
wg_fees <- as.data.frame(data[1]) %>% drop_na() 
wg_fees <- wg_fees[c(4, 8, 10), -1]

wg_fees_cleaned <- gather(wg_fees, key="Room.Type", value="Total")

#change price related columns to numeric
wg_fees_cleaned$Total <- gsub("\\$" ,"", 
                  gsub("\\.00", "", 
                    gsub(",", "", wg_fees_cleaned$Total)))

wg_fees_cleaned$Total <- as.numeric(wg_fees_cleaned$Total)

#change the currency
wg_fees_cleaned$Total <- wg_fees_cleaned$Total/ 0.98

#clean room type col
wg_fees_cleaned$Room.Type <- gsub("\\.", " ", 
                                  gsub("NULL.", "", wg_fees_cleaned$Room.Type))
wg_fees_cleaned$Type <- c("Winter Session Contract", "Term 1 Only", "Term 2 Only")

wg_fees_cleaned$Accom <- "Walter Gage"
  
#final dataframe
head(wg_fees_cleaned, 5)

```

# To compile all the Prices Data
```{r}

#a list of tables to merge
tables_to_merge <- list(oc_fees, pv_fees, tp_fees, bc_fees_cleaned, exchange_fees_cleaned, fc_fees_cleaned, fh_fees, ih_fees_cleaned, md_fees_cleaned, pc_fees_cleaned, sw_fees_cleaned, r_fees_cleaned, tb_fees, wg_fees_cleaned)

#use Reduce to iteratively merge the tables
merged_table <- Reduce(function(x, y) merge(x, y, all = TRUE), tables_to_merge)

#empty types are year round
merged_table[is.na(merged_table$Type), ]$Type <- "Year Round"

#compute the number of months
mevrged_table$Months <- ifelse(merged_table$Type == "Year Round", 12, 
                              ifelse(merged_table$Type == "Term 1 Only", 4, 
                                     ifelse(merged_table$Type == "Term 2 Only", 4, 
                                            ifelse(merged_table$Type == "Winter Session Contract", 8, NA))))

#final prices table, export to csv
write.csv(merged_table, "UBC_Prices_Complied.csv")
```

